% $Header$
% $Author: fager $
% $Date: 2005-02-22 08:31:00 +0100 (Tue, 22 Feb 2005) $
% $Revision: 239 $
% $Log$
% Revision 1.3  2005/02/22 07:31:00  fager
% Corrections from M.Kelly implemented
%
% Revision 1.2  2004/10/21 18:59:06  fager
% Version logging added. Comments from KA implemented.
%

\section{Sweeps of measurements}\label{sec:sweeps}
Milou has not only functionality to handle single measurements,
using the \verb"meassp" class, but also a series of measurements.
Typically, this is a series of measurements obtained at different
bias points. The class used to handle these swept measurements is
called \verb"meassweep".

Milou can create \verb"meassweep" objects from either a directory
with multiple TouchStone files or from an MDIF file\footnote{See
Agilent ADS documentation for details about the MDIF file
format.}.

\subsection{Importing multiple Touchstone files}
Multiple TouchStone files are imported into an \verb"meassweep"
object using the function \verb"read_milousweep". The following
example shows a typical call with this function:
\begin{small}
\begin{verbatim}
    >> sweep = read_milousweep(meassweep,...
        'matlab_milou\test\d0509_all','d0506_','')
    Measurement info
        Date : 20-Oct-2004 19:06:00
        Origin : matlab_milou\test\d0509_fix\d0506_*
        Operator :
        Info :
    Sweep info
        Vgs,min: -0.500000
        Vgs,max: 0.200000
        Vds,min: 0.500000
        Vds,max: 1.500000
        Igs,min: -0.000001
        Igs,max: 0.000002
        Ids,min: 0.003438
        Ids,max: 0.029725
        Freq,min: 1000000000.000000
        Freq,max: 50000000000.000000
        Number of measurements: 24
\end{verbatim}
\end{small}
Please consult \verb">> help read_milousweep" to find the details
on how to call this function.

\subsection{Importing MDIF-files}
MDIF files allow a convenient way of transferring multi
dimensional data to and from Agilent ADS. The structure of the
MDIF files are described in the Agilent ADS manual and not
repeated here.

The function \verb"read_mdif" can be used to import MDIF data into
a \verb"meassweep" object in Milou. It should be stressed that, at
the time of writing, this function is still under development and
may not operate as expected!

\subsection{Importing Maury ATS swept bias S-parameters}
The function \verb"read_s2b" allows Milou to import swept bias
S-parameter files created by the Maury Microwave ATS software.
Please consult the on-line help for more information about this
function.

\subsection{Accessing and indexing meassweep objects}
A \verb"meassweep" object can thought of as a vector of
\verb"meassp" objects. An individual \verb"meassweep" object, or a
subset of the \verb"meassweep" can be accessed using the
parenthesis \verb"()" operator,
\begin{small}
\begin{verbatim}
    >> sweep(1)
        Measurement info
            Date : 2002-10-24, 19:23
            Origin : matlab_milou\test\d0509_all\d0506_0
            Operator :
            Info :
        Measurement state
            MeasType:   SP
            Vgs:    -0.5
            Vds:    0.5
            Igs:    -6.43067E-007
            Ids:    0.00343814
            Freq,min:   1E+009
            Freq,max:   5E+010
        Measurement Data
        xparam-object
            type:  S
            reference: 50
            ports: 2
            elements:  101
    >> sweep(1:10)
    Measurement info
        Date : 20-Oct-2004 19:09:39
        Origin : matlab_milou\test\d0509_all\d0506_*
        Operator :
        Info :
    Sweep info
        Vgs,min: -0.500000
        Vgs,max: 0.200000
        Vds,min: 0.500000
        Vds,max: 1.000000
        Igs,min: -0.000001
        Igs,max: 0.000001
        Ids,min: 0.003438
        Ids,max: 0.023394
        Freq,min: 1000000000.000000
        Freq,max: 50000000000.000000
        Number of measurements: 10
\end{verbatim}
\end{small}

\subsection{The dot-operator}
An individual parameter of the sweep objects can be accessed using
the dot-operator. The following example shows how to access the
\verb"Vgs"-parameter and also how this can be used to use reduce
the sweep-object to contain only bias points with \verb"Vgs" $=0$.
\begin{small}
\begin{verbatim}
    >> sweep.Vgs
    ans =
    Columns 1 through 7
    -0.5000   -0.4000   -0.3000   -0.2000   -0.1000   -0.0000    0.1000
    Columns 8 through 14
        0.2000   -0.5000   -0.4000   -0.3000   -0.2000   -0.1000   -0.0000
    ...

    >> bias_index = find(abs(sweep.Vgs)<0.01);
    >> sweep(bias_index)
    Measurement info
        Date : 20-Oct-2004 19:09:39
        Origin : matlab_milou\test\d0509_all\d0506_*
        Operator :
        Info :
    Sweep info
        Vgs: -0.000000
        Vds,min: 0.500000
        Vds,max: 1.500000
        Igs,min: -0.000000
        Igs,max: -0.000000
        Ids,min: 0.021219
        Ids,max: 0.025760
        Freq,min: 1000000000.000000
        Freq,max: 50000000000.000000
        Number of measurements: 3
\end{verbatim}
\end{small}

\subsection{Adding measurements}
Single measurements can be added to the \verb"meassweep" object
with the \verb"add" function,

\begin{small}
\begin{verbatim}
    >> msp = read_touchstone(meassp,'test\d0509\d0509_20');
    >> sweep_total = add(sweep,msp);
    >> length(sweep_total)-length(sweep)
    ans =
        1
\end{verbatim}
\end{small}
The same function, \verb"add", can also be used to merge two
\verb"meassweep" objects.

\subsection{Writing swept data}
For the moment, no functions have been implemented to write a
\verb"meassweep" object to multiple TouchStone files or into an
MDIF-file.
